Influence of Connectivity on Dung Beetle Communities

### 2025-06-20 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
some writing

Corridors have been shown to be an important mechanism for for minimizing negative consequences of fragmentation [@haddad_corridor_2003]. By improving habitat structure to help facilitate dispersal, wildlife corridors inform movement dynamics of local populations and can shape land uses and occupancy [@forman_general_1995]. *[**EB edit:** break this next sentence into 3 to carry reader though the logic: changes in species diverstiy are important to understand because species are involved in interactions. If we gain or lose species we could gain or lose interactions and resulting ecosystems processes. there is some evidence of this, but... look at the green text notes below]* Because of this dynamic it becomes necessary to understand responses by species compositions at all taxonomic levels and potential trophic cascades resulting from changes in habitat structure and connectivity [@debinski_survey_2000].

>>>>

Corridors have been shown to be an important mechanism for for minimizing negative consequences of fragmentation [@haddad_corridor_2003]. By improving habitat structure to help facilitate dispersal, wildlife corridors inform movement dynamics of local populations and can shape land uses and occupancy [@forman_general_1995]. *[**EB edit:** break this next sentence into 3 to carry reader though the logic: changes in species diverstiy are important to understand because species are involved in interactions. If we gain or lose species we could gain or lose interactions and resulting ecosystems processes. there is some evidence of this, but... look at the green text notes below]*

The resulting changes in species composition are important to identify because

Because of this dynamic it becomes necessary to understand responses by species compositions at all taxonomic levels and potential trophic cascades resulting from changes in habitat structure and connectivity [@debinski_survey_2000].
